Cover letter for ``Two applications\dots''

### 2021-03-08 papers/types2020/revisions/conc.tex
some ednote in conc.tex examples reveisted with new kernel todo updated

There are many avenues of developments for this line of research.
The code reported in Fig.~\ref{fig:augmented} is somewhat idealized in
so far that we omitted a rule performing weak-head reduction (allowing
to handle directly existential goals) and more importantly one that uses
 Elpi's \emph{delay} mechanism. % This a distinguished feature of Elpi, whose
% usef has been advocated in ~\cite{DunchevCT16,coen19mscs}.
The
use of constraints for data generation is well
developed~\cite{FioravantiPS15} and we could try to leverage it to
improve our PBT tactic so that it can use partially instantiated terms: for example generating
say lists with at least two elements as \texttt{[1,2|Tail]}, without
recurring to needed narrowing as in 
LazySmallCheck~\cite{smallcheck}. On the more practical side, it would be worthwhile to investigate \emph{random} generation, following the ideas in~\cite{pltredexconstraintlogic,blanco19ppdp}.

Another current limitation of our PBT tactic is that it does not
handle conversion within an inductive relation. One way to address
this is to have the \emph{init} rule use Coq's unification rather than
\lP's, via Coq-Elpi's \lsti{coq.unif-eq} hook.
%We plan to tackle this either at the Ltac level by co-routining it with simplification tactics and/or by adding rewriting features to our FPC system~\cite{ChihaniM16}.
% Mention \emph{Harpoon}, Beluga's new tactic language?

@@

 \smallskip
 The source files mentioned in this paper are available at \url{https://github.com/proofcert/fpc-elpi}.

>>>>

There are many avenues of developments for this line of research.
The code reported in Fig.~\ref{fig:augmented} is somewhat idealized in
so far that we omitted a rule performing weak-head reduction (allowing
to handle directly existential goals) and more importantly one that uses
 Elpi's \emph{delay} mechanism.\ednote{This may not be accurate anymore -am} % This a distinguished feature of Elpi, whose
% usef has been advocated in ~\cite{DunchevCT16,coen19mscs}.
The
use of constraints for data generation is well
developed~\cite{FioravantiPS15} and we could try to leverage it to
improve our PBT tactic so that it can use partially instantiated terms: for example generating
say lists with at least two elements as \texttt{[1,2|Tail]}, without
recurring to needed narrowing as in 
LazySmallCheck~\cite{smallcheck}. On the more practical side, it would be worthwhile to investigate \emph{random} generation, following the ideas in~\cite{pltredexconstraintlogic,blanco19ppdp}.

% Another current limitation of our PBT tactic is that it does not
% handle conversion within an inductive relation. One way to address
% this is to have the \emph{init} rule use Coq's unification rather than
% \lP's, via Coq-Elpi's \lsti{coq.unif-eq} hook.
%We plan to tackle this either at the Ltac level by co-routining it with simplification tactics and/or by adding rewriting features to our FPC system~\cite{ChihaniM16}.
% Mention \emph{Harpoon}, Beluga's new tactic language?

@@

 \smallskip
 The source files mentioned in this paper are available at \url{https://github.com/proofcert/fpc-elpi}.\ednote{Or not. Fix this -am}

### 2021-03-08 papers/types2020/revisions/elab.tex
some ednote in conc.tex examples reveisted with new kernel todo updated

Continuing with the previous example, consider an external theorem
prover for propositional intuitionistic logic which returns proof
structures as untyped $\lambda$-terms using De Bruijn's notation.
Using the FPC provided in Figure~\ref{fig:debruijn} and the proof
certificate checker in the file \verb+ljf-dep.mod+ of the repository
\url{https://github.com/proofcert/fpc-elpi}, the De Bruijn term
displayed above can be elaborated into a proper proof for the
following Coq theorem.

>>>>

Continuing with the previous example, consider an external theorem
prover for propositional intuitionistic logic which returns proof
structures as untyped $\lambda$-terms using De Bruijn's notation.
Using the FPC provided in Figure~\ref{fig:debruijn} and the proof
certificate checker in the file \verb+ljf-dep.mod+,
%% may nobe this repo -am
%%of the repository \url{https://github.com/proofcert/fpc-elpi},
the De Bruijn term
displayed above can be elaborated into a proper proof for the
following Coq theorem.
